\begin{center}
    {\Large\bfseries\sffamily  Acknowledgements}
\end{center}
    
First and foremost, I thank Prof. Jan M. Rost for granting me the opportunity to be a part of this project. My tenure at PKS has been an incredibly positive and enriching experience that I will always cherish. The journey through this endeavor would have been unimaginably difficult without the guidance of Dr. Sebastian Gemshiem. I am profoundly grateful to him for his countless hours of discussing and mentoring me during my time at PKS. His impact on me goes beyond academics.


I thank Dr. Abhishek Chauduri for his consistent support, inspirational teachings, and mentorship during my tenure at IISER Mohali and for his guidance as my local supervisor. Attending his electrodynamics lectures was a pleasure, and he has consistently been a source of inspiration for me. I am also grateful to Dr. Ambresh Shivaji and Dr. Ramandeep S. Johal for their valuable contributions as members of my thesis committee. Dr. Ambresh's Special Topics in Particle Physics class was the highlight of my academic journey at IISER Mohali, and I truly valued his engaging lectures. Special thanks to Dr. K.P. Yogendran for his mentorship, insightful discussions post-lectures, and guidance, which I thoroughly enjoyed. I also thank Dr. Poonia for his support and for going above and beyond as a supervisor. A special mention of gratitude to Dr. Matthew Eiles for his mentorship and understanding during my time at PKS.

I appreciate the Department of Science and Technology (DST), Government of India, for supporting my academic journey through the INSPIRE Scholarship. I extend my thanks to the Computing and Library staff at IISER Mohali for providing the necessary infrastructure throughout my academic pursuit. I also acknowledge the diligent campus workers who maintained a clean environment and enhanced our overall experience.

The presence of numerous friends at IISER and PKS illuminated my journey with joy and camaraderie. While I could dedicate another thesis to express my gratitude to them, I will keep it concise due to printing costs :-)) ! Special thanks to everyone from JC\&B, Khanabadosh, Baki19, Abir, Dishant, and Anshul. A special mention to Manpreet for his kindness and support throughout our years at IISER and to Pratiyush for being an exceptional roommate and a great colleague. It was a pleasure sharing a room with you, and I appreciate your patience despite my occasional annoyances. I apologize to those whose names I haven't individually mentioned; acknowledging each would require another thesis.

I am thankful to all my friends at PKS for making my time there truly enjoyable. Special thanks to Benjamin for assisting me during my initial days at PKS and the insightful discussions over coffee. I thank Milena for introducing me to the breathtaking hikes in Sächsische Schweiz, along with the delightful cakes and cookies. To Siddarth, your presence has been truly inspiring. To Anish and Suraj, our friendship since childhood is cherished, and I look forward to nurturing this bond further. To Tanu, who has been not just a friend but also a teacher, I have gained valuable life lessons from you, and I hope our bond remains and grows stronger with time.

My deepest and most sincere appreciation goes to my parents. Their unconditional love, unwavering support, and endless encouragement have been my foundation. They believed in me when I doubted myself and motivated me to strive for greater heights. I attribute all that I am and all that I have achieved to them. 


\vspace{1cm}

\hfill -- Aditya Dev

\newpage