\chapter{Introduction\label{chap:introduction}}

\epigraph{ \myopeningquote Time is an illusion \myclosingquote}{-- Albert Einstein}

The unification of Quantum Mechanics and General Relativity has long been the Holy Grail of physics 
since their development. Despite extensive research, no satisfactory theory has yet been proposed 
to solve this challenge. General relativity states that a physical theory should not depend on 
background structures. However, conventional quantization methods often introduce background structures, 
such as imposing the canonical commutation relations on a constant-time hypersurface. The Hamiltonian 
of a generally covariant theory, such as general relativity, is constrained to vanish in the absence 
of boundaries~\cite{gielen2023quantum}. Attempts to quantize gravity using canonical quantization 
lead to a Hamiltonian constraint, known as the Wheeler-DeWitt equation (i.e., \(\oper{H} \ketPsi = 0\)). 
This gives rise to a well-known issue referred to as the ``Problem of Time" within the canonical 
approach to quantum gravity. Further details regarding the Problem of Time are elaborated in 
\refapp{appen:problemoftime}. The issue is that quantum 
states of space-time (and matter in it) do not seem to undergo any time evolution, as dictated by 
the constraints of the theory.

In quantum cosmology, the universe is described by a wave function whose dynamics are governed 
by the Wheeler-DeWitt equation, the quantized Hamiltonian constraint of the system. Due to inherent 
mathematical ambiguities in the Wheeler-DeWitt equation, it is often unreliable to extend beyond the 
semiclassical approximation~\cite{cooke2010qcintro}. The wave function in this approximation is provided 
by the WKB wave function, \(\Psi_{\mathrm{WKB}} 
\approx \exp\left[iS_0/\hbar\right]\psi(\{x_n\})\); where \(S_0\) is a function which obeys the classical
Hamilton-Jacobi equation for the gravitational field~\cite{gielen2023quantum}. Then, we substitute this
WKB ansatz into the Wheeler-DeWitt equation, and applying the relevant approximations leads to the 
time-dependent Schr\"odinger equation. The work of Briggs et al.~\cite{briggs2001derivation} 
has proposed a similar solution to the problem, but from an atomic and molecular physics perspective, 
and their approach is discussed in \refchap{chap:briggs_rost_semiclassic} and \refchap{chap:braun_briggs_jaynes}.
Their approach derives the time dependence by partitioning the entire system into a ``quantum'' system and a classical
environment, with the latter governed by the Hamilton-Jacobi equation. The time dependence is introduced into the
description as a classical parameter.

On the other hand, for locally relativistic quantum field theories, it has been demonstrated that the
long-range Coulomb field causes the total ``charge" operator to commute with all quasi-local observables, 
implying a superselection rule for charges~\cite{Strocchi:1974xh} [refer to \refapp{appen:superselection}
for further details]. Analogously, due to the coupling of energy with the long-range gravitational
field, there is speculation about the existence of a superselection rule for energy~\cite{page1983evolution}. 
This implies that only operators that commute with the Hamiltonian can be observable. However, such 
observables are stationary (i.e., constants of motion). How can we observe time evolution if the 
only observables we can observe are stationary, i.e., they do not evolve at all?

One can argue and ask why one should consider time a fundamental property; rather, what if 
it's an emergent property of a more fundamental theory of the universe? The above arguments and 
problems discussed hint toward a more fundamental nature of time. One approach is to argue that 
the problem of time is a manifestation of background independence rather than the ``timelessness." 
of quantum mechanics, and means that physical states do not evolve relative to an external background 
time. Instead, time evolution must be extracted relationally, by selecting certain quantized degrees 
of freedom to serve as an internal timekeeper, or in other words, pick some quantized degrees of freedom to serve 
as an internal time~\cite{hohn2021trinity}.

Even in our everyday ``classical" world, we never directly measure time; instead, we measure the 
position or angular displacement of a pendulum or a dial and use that measurement to \emph{define} a 
unit of time. The use of relational time in Quantum Mechanics is a framework in which one promotes 
all variables to quantum operators and later chooses one of the variables to operate like a    
``clock" degree of freedom~\cite{gambini2006relational}.

Apart from the semiclassical approaches employed in quantum cosmology, various other avenues 
exist to address the time problem from a purely quantum mechanical standpoint~\cite{hohn2021trinity}. 
One such approach is the ``Page-Wootters Formalism" (abbreviated P\&W formalism), which defines 
relational dynamics in terms of conditional probabilities for the clock and evolving degrees of 
freedom~\cite{page1983evolution}. To date, no one has successfully tackled the problem involving 
general interaction potentials [with the exception of~\cite{Smith:2017pwx} to a certain extent]. 
The original formulation due to P\&W is no exception, as it also neglects the interaction between 
the environment and the system. However, recent work by Gemsheim and Rost has developed a relational 
formalism based on the P\&W formalism, which now includes the environment-system 
interaction~\cite{Gemsheim:2023izg}. This advancement provides the necessary tools to study 
relational dynamics for a general system-environment setting. Their approach is discussed in 
detail in \refchap{chap:sebgem_Rel}. The primary objective of this work is to investigate the transition from a quantum mechanical 
relational description to the classical limit. The concept of a ``large" or semiclassical 
environment will be further elucidated in subsequent chapters, specifically in 
\refchap{chap:braun_briggs_jaynes} and \refchap{chap:briggs_rost_semiclassic}. 
Moreover, this chapter will also delve into the emergence of time dependence within the context of our model system, employing coherent states.

Coherent states hold a significant position in quantum mechanics due to their close 
resemblance to classical states. Thus, it is unsurprising that coherent states 
emerged as the most suitable candidates for representing clock states within our 
relational description. We will explore their properties and relevance 
to our model in incoming chapters.

Finally, \refchap{chap5:RDQ_JCM_chap} will delve into the quantum relational 
description of our model system, building upon the methods outlined in 
\refchap{chap:sebgem_Rel}, and will address the transition to the semiclassical 
limits as discussed in \refchap{chap:braun_briggs_jaynes} and identify the conditions one requires for treating the environment classically.

\newpage